Adaptive Shrinkage Illustration

### 2015-09-30 examples/adaptive_shrinkage.rmd
update paper and dsc-shrink

We simulate from two scenarios, the first with effects more peaked about zero, the second with effects less peaked.
```{r initialize}
set.seed(100)
library(ashr)

#load the simulation function, (rnormmix_datamaker)
source("../dsc-shrink/datamakers/datamaker.R")

@@

```{r plotting}
df = data.frame(betahat = c(sim.spiky$input$betahat,sim.bignormal$input$betahat),
                beta_est = c(beta.spiky.ash$PosteriorMean, beta.bignormal.ash$PosteriorMean),
                lfsr = c(beta.spiky.ash$lfsr, beta.bignormal.ash$lfsr),
                s=c(s,s),
                scenario=c(rep("spiky",NSAMP),rep("big-normal",NSAMP)))
df$signif = df$lfsr<0.05
library(ggplot2)
library(scales)
ggplot(df,aes(x=betahat,y=beta_est,color=1/s)) + 
  xlab("Observed beta-hat") +
  ylab("Shrunken beta estimate") + geom_point() +  facet_grid(.~scenario) + geom_abline(intercept=0,slope=1) +
scale_colour_gradient2(midpoint = median(1/s),low="blue", mid="white",high="red")  +coord_fixed(ratio=1)
ggsave("ash.pdf")
```

```{r}
  ggplot(df,aes(x=pnorm(-abs(betahat/s)),y=lfsr,color=log(s))) + geom_point() +  facet_grid(.~scenario) +xlim(c(0, 0.025)) + xlab("p value") + ylab("lfsr") +
  scale_colour_gradient2(midpoint = 0,low="blue", mid="white",high="red")  
```

```{r}
hist(s,main="histogram of standard errors")
summary(s)
```

@@

>>>>

We simulate from two scenarios, the first with effects more peaked about zero, the second with effects less peaked.
```{r initialize}
set.seed(100)
library(ashr)
library(ggplot2)
library(scales)
#load the simulation function, (rnormmix_datamaker)
source("../dsc-shrink/datamakers/datamaker.R")

@@

```{r plotting}
make_df_for_ashplot = function(sim1,sim2,ash1,ash2,name1="spiky",name2="big-normal"){
  df = data.frame(betahat = c(sim1$input$betahat,sim2$input$betahat),
                beta_est = c(ash1$PosteriorMean, ash2$PosteriorMean),
                lfsr = c(ash1$lfsr, ash2$lfsr),
                s=c(sim1$input$sebetahat,sim2$input$sebetahat),
                scenario=c(rep(name1,NSAMP),rep(name2,NSAMP)))
  df$signif = df$lfsr<0.05
  return(df)
}

ashplot=function(df,xlab="Observed beta-hat",ylab="Shrunken beta estimate"){
  ggplot(df,aes(x=betahat,y=beta_est,color=1/s)) + 
    xlab(xlab) +
    ylab(ylab) + geom_point() +  facet_grid(.~scenario) +   geom_abline(intercept=0,slope=1) +
  scale_colour_gradient2(midpoint = median(1/s),low="blue", mid="white",high="red",space="Lab")  +coord_fixed(ratio=1)
}
df=make_df_for_ashplot(sim.spiky,sim.bignormal,beta.spiky.ash,beta.bignormal.ash)
ashplot(df)
ggsave("ash.pdf")
```

A related consequence is that significance of each observation is no longer monotonic with $p$ value.

```{r}
pval_plot=function(df){
  ggplot(df,aes(x=pnorm(-abs(betahat/s)),y=lfsr,color=log(s))) + geom_point() +  facet_grid(.~scenario) +xlim(c(0, 0.025)) + xlab("p value") + ylab("lfsr") +
  scale_colour_gradient2(midpoint = 0,low="blue", mid="white",high="red")  
}
pval_plot(df)
```

Let's see how these are affected by changing the modelling assumptions so that
the standardized beta are exchangeable (rather than the beta being exchangeable).
```{r run-ash-ES}
beta.bignormal.ash.ES = ash(sim.bignormal$input$betahat, s,model="ES",mixcompdist="normal")
beta.spiky.ash.ES = ash(sim.spiky$input$betahat, s,model="ES",mixcompdist="normal")
df.ES = make_df_for_ashplot(sim.spiky,sim.bignormal,beta.spiky.ash.ES,beta.bignormal.ash.ES)
ashplot(df.ES,ylab="Shrunken beta estimate (ES model)")
pval_plot(df.ES)
```

@@

```{r sehist}
hist(s,main="histogram of standard errors")
summary(s)
```
